Long-range Interatomic Coulombic Decay in ArXe clusters: Experiment and Theory

### 2016-06-09 intro.tex
take care of C-Ne

By definition, ICD is particularly sensitive to the chemical 
environment of the atom or molecule in which the primary 
excitation has taken place. We suggest that this property of ICD 
decay spectra can be used to derive information on a nanoparticle 
or a solvation system, for example. We report here about studies 
in which we produced heterogeneous clusters of the noble gases Ar 
and Xe with different sizes, and compositions ranging from a few 
Xe dopant atoms in an Ar matrix to clusters containing an equal 
amount of both species. By the use of electron-electron 
coincidence spectroscopy and of theoretical simulations on 
prototypical systems we show how the radiationless decay spectrum 
of Ar inner valence (3s) ionized states connects to the structure 
of the clusters.

@@

Soon after, related 
autoionization processes were discovered that proceed via a 
charge transfer instead of an energy transfer. 
These were termed `Electron Transfer Mediated Decay' 
 (ETMD),\cite{zobeley,mueller,sakai,foerstel} for transitions in 
 which the originally excited site is neutralized by the decay.
 and `exchange ICD' for charge transfer contributions to the 
 normal ICD amplitude.\cite{santrarev,jahnkesat}
We find that both energy and charge transfer induced 
autoionization play a role in Ar-Xe, and will detail the 
relevant processes below. The notion of ICD requires that the 
electronic orbitals of the two sites can be distinguished, which 
typically is the case in weakly bonded systems, held together by 
hydrogen bonds or van-der-Waals bonds. In the case of strong
(covalent or metallic) bonding, it is impossible to make a
distinction between ICD and Auger decay.\cite{hergenhahn_review}

>>>>

By definition, ICD is particularly sensitive to the chemical 
environment of the atom or molecule in which the primary 
excitation has taken place. We suggest that this property of ICD 
decay spectra can be used to derive information on a nanoparticle 
or a solvation system, for example. 
Here, the term excitation is used in a broader sense---in the
systems we consider in this work, ICD occurs from an excited, singly 
charged Ar state created by photoionization.
In other systems, ICD was also observed from neutral excited
states and states with more than one vacancy.

We report here about studies 
in which we produced heterogeneous clusters of the noble gases Ar 
and Xe with different sizes, and compositions ranging from a few 
Xe dopant atoms in an Ar matrix to clusters containing an equal 
amount of both species. By the use of electron-electron 
coincidence spectroscopy and of theoretical simulations on 
prototypical systems we show how the radiationless decay spectrum 
of Ar inner valence (3s) ionized states connects to the structure 
of the clusters.

@@

Soon after, related 
autoionization processes were discovered that proceed via a 
charge transfer instead of an energy transfer. 
These were termed `Electron Transfer Mediated Decay' 
 (ETMD),\cite{zobeley,mueller,sakai,foerstel} for transitions in 
 which the originally excited site is neutralized by the decay 
and `exchange ICD' for charge transfer contributions to the 
normal ICD amplitude.\cite{santrarev,jahnkesat}
We find that both energy and charge transfer induced 
autoionization play a role in Ar-Xe, and will detail the 
relevant processes below. The notion of ICD requires that the 
electronic orbitals of the two sites can be distinguished, which 
typically is the case in weakly bonded systems, held together by 
hydrogen bonds or van-der-Waals bonds. In the case of strong
(covalent or metallic) bonding, it is impossible to make a
distinction between ICD and Auger decay.\cite{hergenhahn_review}
